---
title: "Week11"
author: "Vivian Kong"
date: "4/18/2018"
output: html_document
---

```{r}
library(ggplot2)
data(cars)
head(cars)
summary(cars)
```

# Visualize the data

```{r}
carslm <- lm(cars$dist ~ cars$speed)
carslm
plot(cars$speed,cars$dist, main ="speed vs. stopping distance", xlab="speed", ylab="stopping distance")
abline(carslm)
```

# Quality Evaluation

```{r}
summary(carslm)
```

##According to the textbook, we know that if the line is a good fit with the data, the median value of residual is near zero, min and max values of roughly the same magnitude. For this model, the median is -2.272 which is preety close to 0, min and max is similar magnitude. Also, for a good linear model, standard error for each coefficients that is at least 5 to 10 times smaller than the corresponding coefficent. For the standard error for speed is (3.9324/0.4155=9.4642) This ratio fits the category we are talking about. For the p-value of the coefficient is 1.49e-12, a tiny value - the probability is not relevant in this model. It indicates the model fits pretty well. 

# Residual Analysis

```{r}
plot(fitted(carslm),resid(carslm))
```

##In this plot, we see the residuals roughly cluster around 0 which indicates the model is relatively good fit. 

```{r}
qqnorm(resid(carslm))
qqline(resid(carslm))
```

##We know that if the residuals were normally distributed, we would expect the points follow a straight line. In our model, we can see that most points follow the straight line. It also indicates that the linear model is reliable.
