---
title: "Week 15"
author: "Vivian Kong"
date: "5/14/2018"
output: html_document
---

1.The distance formula is: $D= \sum_{i=1}^{n}(y_i-(ax_i+b))^2$ 

To find the least square regression line. We need to take the first partial derivative to solve for a and b. $\frac{dD}{da}=\sum_{i=1}^{n}(2(y_i-ax_i-b)(-x_i)=0$  $\frac{dD}{db}=\sum_{i=1}^{n}2(y_i-ax_i-b)(-1)=0$  
 
Equation 1: $a\sum_{i=1}^{n}(x_i)^2+b\sum_{i=1}^{n} x_i=\sum_{i=1}^{n}x_iy_i$ 

Equation 2: $a\sum_{i=1}^{n}(x_i)+nb=\sum_{i=1}^{n}y_i$

Plug in the points, we get equation 1: $249.9a+35b=545.86$  equation 2:$35a+5b=75$

```{r}
library("pracma")
A <- matrix(c(249.9, 35, 545.86, 35, 5, 75),2,3,byrow=TRUE)
rref(A)
```
So, $y=4.26x-14.8$

2.Find local max/min or saddle, we need to take partial derivative $\frac {df}{dx}=24-6y^2=0, y^2=4, y=-2, 2$  
$\frac{df}{dy}=-12xy-24y^2=0, -12y(x+2y)=0, y=0 (rejected), x=-2y$  
$\frac{d^2f}{dx^2}=0,\frac{d^2f}{dy^2}=-12x-48y, \frac{d^2f}{dxy}=-12y$  
$D(x,y)=f_{xx}f_{yy}-f^2_{xy}=-(-12y)^2=-144y^2. D(x,y)<0$ for all (x,y), so by the Second Derivative Test, any critical point is a saddle point. 
$(-4,2,-64)$ and $(4,-2,64)$ are saddle points. 

3. Step 1 $R(x,y)=x(81-21x+17y)+y(40+11x-23y)$  
Step 2. Evaluate
```{r}
eval( 2.30*(81-21*2.30+17*4.1)+4.1*(40+11*2.3-23*4.1))
```
  The revenue is $116.62.

4. $x+y=96, y=96-x$  
$C= \frac{1}{6}x^2+\frac{1}{6}(96-x)^2+7x+25(96-x)+700$  
$C_x=\frac{1}{3}x-\frac{1}{3}(96-x)+7-25=\frac{2}{3}x-50=0, x=75$
Since $C_{xx}=\frac{2}{3}>0$ relative minima, so $x=75, y=21$ LA produces 75, Denver produces 21.

5.  

$\int_{2}^{4}\int_{2}^{4} e^{8x+3y}dxdy$ 

$=\int_{2}^{4}\int_{2}^{4}e^{8x}e^{3y}dxdy$ 

$=\int_{2}^{4} \frac{1}{8}e^{3y} e^{8x} |_2^4dy$ 

$=\frac{1}{8}(e^{32}-e^{16})\int_2^4 e^{3y}dy$ 

$=\frac{1}{8}(e^{32}-e^{16}) \frac{1}{3}e^{3y}|_2^4$ 

$=\frac{1}{24}(e^{32}-e^{16})(e^{12}-e^{6})$