---
title: "HW3 Assignment"
author: "Vivian Kong"
header-includes:
  - \usepackage{amsmath}
date: "2/12/2018"
output: html_document
---

---
# Probelm set 1
# (1)
```{r}
library(matrixcalc)
A <- matrix(c(1,2,3,4,-1,0,1,3,0,1,-2,1,5,4,-2,-3), 4, byrow=T)
A
matrix.rank(A)
```

# (2) If m >n, the maximum rank can be n, and the minimum rank will be 1 since we assume that the matrix is non-zero.

# (3)
```{r}
B <- matrix(c(1,2,1,3,6,3,2,4,2), 3, byrow=T)
B
matrix.rank(B)
```

# Problem set 2

$A=\begin{pmatrix}
1 & 2 & 3\\
0 & 4 & 5\\
0 & 0 & 6\end{pmatrix}$


$x=\begin{pmatrix}
x & 0 & 0\\
0 & x & 0\\
0 & 0 & x\end{pmatrix}$


$A-x=\begin{pmatrix}
1-x & 2 & 3\\
0 & 4-x & 5\\
0 & 0 & 6-x\end{pmatrix}$

$det(A-x)=(1-x)(24-10x+x^2)$

$(1-x)(24-10x+x^2)=0$

$(1-x)(x-4)(x-6)=0$


$x=1,x=4,x=6$


$a) eigenvalue=1$

$B=\begin{pmatrix}
0 & 2 & 3 &| 0\\
0 & 3 & 5 &| 0\\
0 & 0 & 5 &| 0\end{pmatrix}\\
reduced\ rechelon \ form \ B= \begin{pmatrix}
0 & 1 & 0 &| 0\\
0 & 0 & 1 &| 0\\
0 & 0 & 0 &| 0\end{pmatrix}$

$x_2=0, x_3=0, x_1=1$

$\begin{pmatrix}
1 & 2 & 3\\
0 & 4 & 5\\
0 & 0 & 6\end{pmatrix} *
\begin{pmatrix}
1 \\0\\ 0\end{pmatrix}= \begin{pmatrix}
1 \\0\\ 0\end{pmatrix}$

$b) eigenvalue=4$

$C=\begin{pmatrix}
-3 & 2 & 3 &| 0\\
0 & 0 & 5 &| 0\\
0 & 0 & 2 &| 0\end{pmatrix}\\
reduced\ rechelon \ form \ C= \begin{pmatrix}
1 & -2/3 & 0 &| 0\\
0 & 0 & 1 &| 0\\
0 & 0 & 0 &| 0\end{pmatrix}$

$x_1=2, x_2=3, x_3=0$

$\begin{pmatrix}
1 & 2 & 3\\
0 & 4 & 5\\
0 & 0 & 6\end{pmatrix} *
\begin{pmatrix}
2 \\3\\ 0\end{pmatrix}= \begin{pmatrix}
8 \\12\\ 0\end{pmatrix}=4*
\begin{pmatrix}
2 \\ 3\\0\end{pmatrix}$

$c) eigenvalue=6$

$D=\begin{pmatrix}
-5 & 2 & 3 &| 0\\
0 & -2 & 5 &| 0\\
0 & 0 & 0 &| 0\end{pmatrix}\\
reduced\ rechelon \ form \ D= \begin{pmatrix}
1 & 0 & -8/5 &| 0\\
0 & 1 & -5/2 &| 0\\
0 & 0 & 0 &| 0\end{pmatrix}$

$x_1=8/5, x_2=5/2, x_3=1$

$\begin{pmatrix}
1 & 2 & 3\\
0 & 4 & 5\\
0 & 0 & 6\end{pmatrix} *
\begin{pmatrix}
8/5 \\5/2\\ 1\end{pmatrix}= \begin{pmatrix}
9.6 \\15\\ 6\end{pmatrix}=6*
\begin{pmatrix}
8/5 \\ 5/2\\1\end{pmatrix}$

